Enhancement of SDR in Thessaloniki

### 2024-03-14 GHI_enh_04_investigate.tex
Commit 2024-03-12 19:22
Commit 2024-03-13 14:14
Commit 2024-03-14 11:11

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-03-12}

@@

\hypertarget{sza-enhancements}{%
\subsubsection{SZA enhancements}\label{sza-enhancements}}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-3} \end{center}

\hypertarget{sza-enhancements-by-month}{%
\subsubsection{SZA enhancements by month}\label{sza-enhancements-by-month}}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-3} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-9} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-10} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-11} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-12} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-13} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-15} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-16} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-17} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-18} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-19} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-20} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-21} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-22} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-23} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-24} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-25} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-26} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-27} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-28} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-29} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-30} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-31} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-32} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-33} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-34} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-35} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-36} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-37} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-38} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-39} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-40} \end{center}

@@

\begin{verbatim}
2024-03-12 15:10:56.3 athan@tyler GHI_enh_04_investigate.R 2.333127 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-03-14}

@@

@@

\begin{verbatim}
2024-03-14 09:06:31.8 athan@tyler GHI_enh_04_investigate.R 1.124109 mins
\end{verbatim}

### 2024-03-14 GHI_enh_06_sza.tex
Commit 2024-03-14 11:11

\begin{verbatim}
ST_daily ST_E_daily ST_E_daily_seas ST_extreme_daily
\end{verbatim}

@@

\hypertarget{daily-trends}{%
\subsubsection{Daily Trends}\label{daily-trends}}

\begin{verbatim}
Warning in ans * length(l) + if1: longer object length is not a multiple of
shorter object length
\end{verbatim}

\newpage

\begin{verbatim}
Loading required package: stringr
\end{verbatim}

\hypertarget{trends-on-daily-observations-data}{%
\paragraph{Trends on Daily Observations data}\label{trends-on-daily-observations-data}}

Units for GLB\_diff.max : Watt/m\^{}2

lmD: 1.566006 +/- 0.1083205

lmY: 1.566022 +/- 0.1083224

Arima: 1.5664 0.1467 10.6786 0

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-1} \end{center}

Units for GLB\_diff.mean : Watt/m\^{}2

lmD: 0.9508037 +/- 0.1552487

lmY: 0.9508275 +/- 0.1552514

Arima: 1.0223 0.2369 4.3149 0

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-2} \end{center}

Units for GLB\_diff.median : Watt/m\^{}2

lmD: 1.086985 +/- 0.1678711

lmY: 1.087013 +/- 0.1678741

Arima: 1.16 0.2511 4.6198 0

Units for GLB\_diff.N :

lmD: -0.01234536 +/- 0.1388793

lmY: -0.01233011 +/- 0.1388818

\begin{verbatim}
Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
possible convergence problem: optim gave code = 1
\end{verbatim}

\begin{verbatim}
Warning in sqrt(diag(se)): NaNs produced

Warning in sqrt(diag(se)): NaNs produced
\end{verbatim}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-3} \end{center}

Arima: -0.0132 6.9042 -0.0019 0.9985

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-4} \end{center}

Units for GLB\_diff.sum : kJ/m\^{}2

lmD: 33.66024 +/- 5.69273

lmY: 33.6608 +/- 5.692829

Arima: 33.7214 8.8815 3.7968 1e-04

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-5} \end{center}

Units for GLB\_ench.max : Watt/m\^{}2

lmD: 0.003266044 +/- 0.0002706817

lmY: 0.003266077 +/- 0.0002706865

Arima: 0.0033 4e-04 9.0497 0

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-6} \end{center}

Units for GLB\_ench.mean : Watt/m\^{}2

lmD: 0.001714761 +/- 0.0002777697

lmY: 0.001714817 +/- 0.0002777745

Arima: 0.0019 5e-04 4.0604 0

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-7} \end{center}

Units for GLB\_ench.median : Watt/m\^{}2

lmD: 0.001677019 +/- 0.0003136298

lmY: 0.001677082 +/- 0.0003136353

Arima: 0.0018 5e-04 3.615 3e-04

Units for GLB\_ench.N :

lmD: -0.01234536 +/- 0.1388793

lmY: -0.01233011 +/- 0.1388818

\begin{verbatim}
Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
possible convergence problem: optim gave code = 1

Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
NaNs produced

Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
NaNs produced
\end{verbatim}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-8} \end{center}

Arima: -0.0132 6.9042 -0.0019 0.9985

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-9} \end{center}

Units for GLB\_ench.sum : Watt/m\^{}2

lmD: 0.9770065 +/- 0.1439346

lmY: 0.9770288 +/- 0.1439371

Arima: 1.041 0.2186 4.7611 0

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-10} \end{center}

\newpage

\hypertarget{trends-on-daily-enhancements-data}{%
\paragraph{Trends on Daily Enhancements data}\label{trends-on-daily-enhancements-data}}

Units for GLB\_diff.max : Watt/m\^{}2

lmD: 0.8175029 +/- 0.1034317

lmY: 0.8175138 +/- 0.1034336

Arima: 0.8175 0.12 6.8102 0

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-11} \end{center}

Units for GLB\_diff.mean : Watt/m\^{}2

lmD: 0.216071 +/- 0.03807207

lmY: 0.2160751 +/- 0.03807275

Arima: 0.2161 0.0414 5.2169 0

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-12} \end{center}

Units for GLB\_diff.median : Watt/m\^{}2

lmD: 0.190931 +/- 0.03787542

lmY: 0.1909357 +/- 0.03787609

Arima: 0.1909 0.0401 4.7631 0

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-13} \end{center}

Units for GLB\_diff.N :

lmD: 0.4856759 +/- 0.04638817

lmY: 0.4856822 +/- 0.046389

Arima: 0.4857 0.0552 8.802 0

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-14} \end{center}

Units for GLB\_diff.sum : kJ/m\^{}2

lmD: 1.467857 +/- 0.1526559

lmY: 1.46788 +/- 0.1526586

Arima: 1.4679 0.1843 7.9642 0

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-15} \end{center}

Units for GLB\_ench.max : Watt/m\^{}2

lmD: 0.00133588 +/- 0.0001367161

lmY: 0.001335895 +/- 0.0001367186

Arima: 0.0013 2e-04 8.5089 0

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-16} \end{center}

Units for GLB\_ench.mean : Watt/m\^{}2

lmD: 0.0004227125 +/- 5.903165e-05

lmY: 0.0004227187 +/- 5.90327e-05

Arima: 4e-04 1e-04 6.2905 0

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-17} \end{center}

Units for GLB\_ench.median : Watt/m\^{}2

lmD: 0.0003723972 +/- 6.132751e-05

lmY: 0.0003724038 +/- 6.13286e-05

Arima: 4e-04 1e-04 5.4462 0

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-18} \end{center}

Units for GLB\_ench.N :

lmD: 0.4856759 +/- 0.04638817

lmY: 0.4856822 +/- 0.046389

Arima: 0.4857 0.0552 8.802 0

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-19} \end{center}

Units for GLB\_ench.sum : Watt/m\^{}2

lmD: 0.03656091 +/- 0.003621574

lmY: 0.03656153 +/- 0.003621638

Arima: 0.0366 0.0042 8.6966 0

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-20} \end{center}

\newpage

\hypertarget{trends-on-daily-extreme-enhancements-data}{%
\paragraph{Trends on Daily Extreme Enhancements data}\label{trends-on-daily-extreme-enhancements-data}}

Units for GLB\_diff.max : Watt/m\^{}2

lmD: 0.1872084 +/- 0.2494764

lmY: 0.1872455 +/- 0.2494804

Arima: 0.1718 0.3646 0.4711 0.6376

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-21} \end{center}

Units for GLB\_diff.mean : Watt/m\^{}2

lmD: 0.04977389 +/- 0.1925048

lmY: 0.04979834 +/- 0.1925079

Arima: 0.0085 0.3464 0.0247 0.9803

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-22} \end{center}

Units for GLB\_diff.median : Watt/m\^{}2

lmD: 0.0912485 +/- 0.1914527

lmY: 0.09127162 +/- 0.1914558

Arima: 0.05 0.3354 0.149 0.8816

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-23} \end{center}

Units for GLB\_diff.N :

lmD: 0.03034705 +/- 0.02124537

lmY: 0.03034902 +/- 0.02124571

Arima: 0.0304 0.022 1.3788 0.1679

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-24} \end{center}

Units for GLB\_diff.sum : kJ/m\^{}2

lmD: 0.368357 +/- 0.2534977

lmY: 0.3683834 +/- 0.2535018

Arima: 0.3684 0.2583 1.4266 0.1537

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-25} \end{center}

Units for GLB\_ench.max : Watt/m\^{}2

lmD: 0.0005084984 +/- 0.0002811406

lmY: 0.0005085061 +/- 0.0002811451

Arima: 5e-04 3e-04 1.5978 0.1101

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-26} \end{center}

Units for GLB\_ench.mean : Watt/m\^{}2

lmD: 0.000356478 +/- 0.0002141255

lmY: 0.0003564771 +/- 0.0002141289

Arima: 3e-04 3e-04 1.3203 0.1867

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-27} \end{center}

Units for GLB\_ench.median : Watt/m\^{}2

lmD: 0.0003987357 +/- 0.0002210796

lmY: 0.0003987361 +/- 0.0002210831

Arima: 4e-04 3e-04 1.4505 0.1469

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-28} \end{center}

Units for GLB\_ench.N :

lmD: 0.03034705 +/- 0.02124537

lmY: 0.03034902 +/- 0.02124571

Arima: 0.0304 0.022 1.3788 0.1679

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-29} \end{center}

Units for GLB\_ench.sum : Watt/m\^{}2

lmD: 0.008776338 +/- 0.005506711

lmY: 0.00877684 +/- 0.005506799

Arima: 0.0088 0.0057 1.5378 0.1241

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-30} \end{center}

@@

\hypertarget{group-stats}{%
\subsubsection{Group stats}\label{group-stats}}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-1} \end{center}

\begin{verbatim}
Warning in scale_y_log10(): log-10 transformation introduced infinite values.
\end{verbatim}

\begin{verbatim}
Warning: Removed 25 rows containing missing values or values outside the scale
range (`geom_bar()`).
\end{verbatim}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-2} \end{center}

@@

\begin{verbatim}
Warning: The S3 guide system was deprecated in ggplot2 3.5.0.
i It has been replaced by a ggproto system that can be extended.
This warning is displayed once every 8 hours.
Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
\end{verbatim}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-3} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-6} \end{center}

\hypertarget{zhang2018}{%
\subsection{@Zhang2018}\label{zhang2018}}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-8} \end{center}

\begin{verbatim}
Scale for x is already present.
Adding another scale for x, which will replace the existing scale.
\end{verbatim}

\begin{verbatim}
Warning: Removed 5 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-9} \end{center}

\begin{verbatim}
Scale for x is already present.
Adding another scale for x, which will replace the existing scale.
\end{verbatim}

\begin{verbatim}
Warning: Removed 5 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-10} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_N_doy-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climCEmonth-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_month_norm_MAX_N-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_month_norm_MAX_median_N-1} \end{center}

\begin{verbatim}
Warning: The `fun.y` argument of `stat_summary()` is deprecated as of ggplot2 3.3.0.
i Please use the `fun` argument instead.
This warning is displayed once every 8 hours.
Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
\end{verbatim}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_month_norm_MAX_median_N-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climECEmonth-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_ECE_month_norm_MAX_median_N-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_ECE_month_norm_MAX_median_N-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climCE_daily-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climCE_week-1} \end{center}

\hypertarget{energy-contribution-of-enhancements}{%
\subsubsection{Energy contribution of enhancements}\label{energy-contribution-of-enhancements}}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-3} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-7} \end{center}

@Martins2022

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel_energy-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel_energy-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel_energy-3} \end{center}

@@

\begin{verbatim}
2024-03-14 09:06:31.8 athan@tyler GHI_enh_04_investigate.R 1.124109 mins
\end{verbatim}

>>>>

@@

\hypertarget{sza-enhancements}{%
\subsubsection{SZA enhancements}\label{sza-enhancements}}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-3} \end{center}

@@

\hypertarget{sza-enhancements-by-month}{%
\subsubsection{SZA enhancements by month}\label{sza-enhancements-by-month}}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-3} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-9} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-10} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-11} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-12} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-13} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-15} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-16} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-17} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-18} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-19} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-20} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-21} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-22} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-23} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-24} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-25} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-26} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-27} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-28} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-29} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-30} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-31} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-32} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-33} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-34} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-35} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-36} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-37} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-38} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-39} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-40} \end{center}

@@

\begin{verbatim}
2024-03-14 09:10:56.9 athan@tyler GHI_enh_06_sza.R 0.671435 mins
\end{verbatim}
